Supporting Information for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-12-13 Documents/supporting_information.tex
Initial changes for PNAS.

% \usepackage[style=nature]{biblatex}
% \addbibresource{supplementary_information.bib}
\usepackage[sort&compress]{natbib}
\usepackage{hypernat}
\citestyle{nature}

% For Nature, add 27 to reference numbers to start after
% last number in manuscript.
\usepackage{etoolbox}
\makeatletter
\apptocmd{\thebibliography}{\global\c@NAT@ctr 27\relax}{}{}
\makeatother

% For Nature, no page numbers.
\pagestyle{empty}
\usepackage{etoolbox}
\apptocmd{\maketitle}{\thispagestyle{empty}}{}{}

@@

\renewcommand{\thesection}{S\arabic{section}}
\newcommand{\sectionname}{Section}
\renewcommand{\sectionautorefname}{\sectionname}
\renewcommand{\figurename}{Supplementary Fig.}
\renewcommand{\figureautorefname}{\figurename}
\renewcommand{\tablename}{Supplementary Table}
\renewcommand{\tableautorefname}{\tablename}

\title{Supplementary Methods for\\
  \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
    countries}}

@@

\begin{table}
  \begin{center}
    \begin{tabularx}{\textwidth}{lXlll}
      \hline
      & Definition & Value & References \\
      \hline
      $\mu$ & Background death rate
      & Country specific, Supplementary Table 2
      & \cite{World_Development_Indicators2013-ee} \\
      $\kappa$ & Recruitment rate
      & Country specific, Supplementary Table 2
      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
      $\delta$	& Rate of progression from acute infection
      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
      & \cite{Hollingsworth2008-iy} \\
      $\sigma$	& Rate of developing AIDS without viral suppression
      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
      $\theta$ & Rate of developing AIDS with viral suppression
      & Eq.~(\ref{theta}) & --- \\
      $\gamma$ & Rate of viral suppression
      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
      & \cite{Currie2009-yz} \\
      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
      & \cite{Morgan2002-cq} \\
      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
      $\omega$	& Reduction in life expectancy with viral suppression
      & $\Uniform$(5, 8)\;y
      & \cite{Samji2013-kf, Unaids2014-ue} \\
      $\tau_{A}$ & Transmissibility during acute phase
      & $\Triangular$(0.0039, 0.0082, 0.0150)
      & \cite{Wawer2005-us, Skarbinski2015-ni}\\
      $\tau_{U}$ & Transmissibility after acute phase
      & $\Triangular$(0.00077, 0.0014, 0.00251)
      & \cite{Hughes2012-so} \\
      $\epsilon$ & Relative transmissibility with
      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
      & \cite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
        rodger_2016} \\
      $n$ & Coital acts per year & $\Uniform$(96, 108)
      & \cite{Wawer2005-us, Abdool_Karim2010-cm}\\
      $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
      $\phi$ & Treatment rate & See eq.~(\ref{treatment_rate}) & --- \\
      $\psi$ & Rate of relapse to untreated & See eq.~(\ref{relapse_rate})
      & --- \\
      $\zeta$ & Vaccination rate & See eq.~(\ref{vaccination_rate}) & --- \\
      \hline
      \vspace*{-2.5em}
    \end{tabularx}
    \caption{Model parameters. $\Triangular$, $\Uniform$, and
      $\BetaPERT$ are sampling distributions (\autoref{uncertainty}).
      For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and
      $70\%$ were also assessed in sensitivity analysis.}
    \label{model_param}
  \end{center}
\end{table}

@@

The results from the country simulations were aggregated to the
regional and global levels by adding the numbers of people in each
compartment over time and then new infections, per-capita incidence,
PLHIV, and HIV-related deaths were calculated from the aggregates.
(See Supplementary Table 6 for the definitions of UNAIDS regions.)

@@

We found sufficient published estimates and data to parametrize our
model for 127 countries.  Demographic data, including population
growth rate,\cite{WorldBankpg} death
rate,\cite{World_Development_Indicators2013-ee} and number of people
aged 15--49 years\cite{The_World_Bank2016-fd} were obtained from the
World Bank (Supplementary Table 2). Longitudinal HIV prevalence
(Supplementary Table 3) and incidence (Supplementary Table 4)
estimates for ages 15--49, spanning from as early as 1990 for some
countries to 2015, were primarily obtained from the AIDSinfo database
produced by UNAIDS.\cite{Unaids2016-an} Other sources included UNAIDS
Country Progress Reports\cite{Unaids2016-am} published from 2012 to
2016 and AIDS Data Hub,\cite{AIDSdatahub-fg} which compiles data from
UNAIDS, UNICEF, WHO, and the Asian Development Bank.  These sources
were also used to inform the initial conditions for the model
regarding the number of people diagnosed with HIV, the number on ART,
and the number who have viral suppression or have been retained on
treatment for at least 12 months (Supplementary Table 5).  Where data
or estimates were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  Full information on the sources used
for each country is provided in Supplementary Tables 2--5.  These
source tables are also available in our public source-code
repository.\cite{medlock2016-git}

@@

We tailored our model to each of the 127 countries separately.  Using
available historical country-specific estimates of prevalence and
incidence (Supplementary Tables 3 and 4), and published estimates of
transmissibility per coital
act,\cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
  Skarbinski2015-ni}
we derived an average country-specific transmission rate, taking into
account the differential contributions from the proportions of acute,
unsuppressed, and suppressed of the infected population in each
country.  Using historical data to smooth out short-term variations,
our calibration method provided estimates of current country-specific
transmission, as detailed below.

@@

% \printbibliography
\bibliography{supplementary_information}
\bibliographystyle{naturemag}

>>>>

% \usepackage[style=nature]{biblatex}
% \addbibresource{supporting_information.bib}
\usepackage[numbers, round, comma, sort&compress]{natbib}
\usepackage{hypernat}

@@

\renewcommand{\thesection}{S\arabic{section}}
\newcommand{\sectionname}{Section}
\renewcommand{\sectionautorefname}{\sectionname}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

\title{Supporting Information for\\
  \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127
    countries}}

@@

\begin{table}
  \begin{center}
    \begin{tabularx}{\textwidth}{lXlll}
      \hline
      & Definition & Value & References \\
      \hline
      $\mu$ & Background death rate
      & Country specific, Data Table 2
      & \cite{World_Development_Indicators2013-ee} \\
      $\kappa$ & Recruitment rate
      & Country specific, Data Table 2
      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
      $\delta$	& Rate of progression from acute infection
      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
      & \cite{Hollingsworth2008-iy} \\
      $\sigma$	& Rate of developing AIDS without viral suppression
      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
      $\theta$ & Rate of developing AIDS with viral suppression
      & Eq.~(\ref{theta}) & --- \\
      $\gamma$ & Rate of viral suppression
      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
      & \cite{Currie2009-yz} \\
      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
      & \cite{Morgan2002-cq} \\
      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
      $\omega$	& Reduction in life expectancy with viral suppression
      & $\Uniform$(5, 8)\;y
      & \cite{Samji2013-kf, Unaids2014-ue} \\
      $\tau_{A}$ & Transmissibility during acute phase
      & $\Triangular$(0.0039, 0.0082, 0.0150)
      & \cite{Wawer2005-us, Skarbinski2015-ni}\\
      $\tau_{U}$ & Transmissibility after acute phase
      & $\Triangular$(0.00077, 0.0014, 0.00251)
      & \cite{Hughes2012-so} \\
      $\epsilon$ & Relative transmissibility with
      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
      & \cite{Donnell2010-xo, attia_2009, wilson_2012, jia_2013,
        rodger_2016} \\
      $n$ & Coital acts per year & $\Uniform$(96, 108)
      & \cite{Wawer2005-us, Abdool_Karim2010-cm}\\
      $\alpha$ & Diagnosis rate & See eq.~(\ref{diagnosis_rate}) & --- \\
      $\phi$ & Treatment rate & See eq.~(\ref{treatment_rate}) & --- \\
      $\psi$ & Rate of relapse to untreated & See eq.~(\ref{relapse_rate})
      & --- \\
      $\zeta$ & Vaccination rate & See eq.~(\ref{vaccination_rate}) & --- \\
      \hline
      \vspace*{-2.5em}
    \end{tabularx}
    \caption{Model parameters. $\Triangular$, $\Uniform$, and
      $\BetaPERT$ are sampling distributions (\autoref{uncertainty}).
      For vaccine efficacy, $50\%$ was the baseline, and $30\%$ and
      $70\%$ were also assessed in sensitivity analysis.}
    \label{model_param}
  \end{center}
\end{table}

@@

The results from the country simulations were aggregated to the
regional and global levels by adding the numbers of people in each
compartment over time and then new infections, per-capita incidence,
PLHIV, and HIV-related deaths were calculated from the aggregates.
(See Data Table 6 for the definitions of UNAIDS regions.)

@@

We found sufficient published estimates and data to parametrize our
model for 127 countries.  Demographic data, including population
growth rate,\cite{WorldBankpg} death
rate,\cite{World_Development_Indicators2013-ee} and number of people
aged 15--49 years\cite{The_World_Bank2016-fd} were obtained from the
World Bank (Data Table 2). Longitudinal HIV prevalence
(Data Table 3) and incidence (Data Table 4)
estimates for ages 15--49, spanning from as early as 1990 for some
countries to 2015, were primarily obtained from the AIDSinfo database
produced by UNAIDS.\cite{Unaids2016-an} Other sources included UNAIDS
Country Progress Reports\cite{Unaids2016-am} published from 2012 to
2016 and AIDS Data Hub,\cite{AIDSdatahub-fg} which compiles data from
UNAIDS, UNICEF, WHO, and the Asian Development Bank.  These sources
were also used to inform the initial conditions for the model
regarding the number of people diagnosed with HIV, the number on ART,
and the number who have viral suppression or have been retained on
treatment for at least 12 months (Data Table 5).  Where data
or estimates were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  Full information on the sources used
for each country is provided in Data Tables 2--5.  These
source tables are also available in our public source-code
repository.\cite{medlock2016-git}

@@

We tailored our model to each of the 127 countries separately.  Using
available historical country-specific estimates of prevalence and
incidence (Data Tables 3 \& 4), and published estimates of
transmissibility per coital
act,\cite{Wawer2005-us, Donnell2010-xo, Hughes2012-so,
  Skarbinski2015-ni}
we derived an average country-specific transmission rate, taking into
account the differential contributions from the proportions of acute,
unsuppressed, and suppressed of the infected population in each
country.  Using historical data to smooth out short-term variations,
our calibration method provided estimates of current country-specific
transmission, as detailed below.

@@

% \printbibliography
\bibliography{supporting_information}
\bibliographystyle{pnas2011}
